Homelessness and Drug Toxicity

### 2024-03-16 paper/paper.qmd
completed results section, fixed spelling and writing mistakes

library(tidyverse)
library(palmerpenguins)
library(here)
library(bayesplot)

@@

@@

@tbl-sample2 also shows the data associated with cases reported as "death due to drug toxicity". This data however, shows the number of deaths reported for the years 2017 and 2018 for each gender rather than age group.

@@

Define $count_i$ as the count of deaths that resulted from drug toxicity in Toronto. Then $Gender_i$ is the gender for that count of deaths and $Age group_i$ is the range of ages for the count of deaths deaths.

@@

We expect their to be a larger relationship between males and the number of deaths. This is because there are more males within the homeless population and more males homeless as a result of addiction to drugs. These reasons make it clear that that the male relationship is larger than the female.

@@

@age-graph visualizes our first data of interest, showing deaths per year for each age group. Looking at this graph teaches us a few things. Firstly, homeless aged 40-59 are the most prone to death due to drug intoxication, followed by age group 20-39. Secondly, deaths by intoxication peaked during the years 2020-2022, these years are when the pandemic was most prevalent. Lastly, there seems to be no improvement in the homeless drug problem over this time period.

```{r}
#| label: fig-age-graph
#| fig-cap: Deaths Per Year for Age Group
#| echo: false

@@

@fig-gender-graph suggests that males occupy a majority of the homeless population as well as being more prone to drug abuse. This observation explains why we see a much greater number of male deaths compared to females. However, this does not explain why the pandemic affected the male population more greatly than the female population, and why did the death count for the female population drop so drastically for the year 2023? Looking at the @fig-age-graph we can see that during 2023, the age group 20-39 saw a greatest dip pin death count. Coupling this with @fig-gender-graph could suggest that a large number of females from the ages 20-39 saw improvements in deaths due to drug toxicity.

Our results are summarized in @tbl-modelresults. We need a paragraph about this table.

@@

this table is for poisson 
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

can discuss difference in results between them and overall coefficients be care when intrepting coefficients in each model

>>>>

library(tidyverse)
library(here)
library(bayesplot)

@@

## Measurement and Variables of Interest

@@

@tbl-sample2 also shows the data associated with cases reported as "death due to drug toxicity". This data however, shows the number of deaths reported for the years 2017-2020 for each gender rather than age group.

@@

Define $count_i$ as the count of deaths that resulted from drug toxicity in Toronto. Then $Gender_i$ is the gender for that count of deaths and $Age group_i$ is the range of ages for the count of deaths.

@@

We expect there to be a larger relationship between males and the number of deaths. This is because there are more males within the homeless population and more males homeless as a result of addiction to drugs. These reasons make it clear that that the male relationship is larger than the female.

@@

@fig-age-graph visualizes our first data of interest, showing deaths per year for each age group. Looking at this graph teaches us a few things. Firstly, homeless aged 40-59 are the most prone to death due to drug intoxication, followed by age group 20-39. Secondly, deaths by intoxication peaked during the years 2020-2022, these years are when the pandemic was most prevalent. Lastly, there seems to be no improvement in the homeless drug problem over this time period.

```{r}
#| label: fig-age-graph
#| fig-cap: Deaths Per Year per Age Group
#| echo: false

@@

@fig-gender-graph suggests that males occupy a majority of the homeless population as well as being more prone to drug abuse. This observation explains why we see a much greater number of male deaths compared to females. However, this does not explain why the pandemic affected the male population more greatly than the female population, and why did the death count for the female population drop so drastically for the year 2023? Looking at the @fig-age-graph we can see that during 2023, the age group 20-39 saw the greatest dip in death count. Coupling this with @fig-gender-graph could suggest that a large number of females from the ages 20-39 saw improvements in deaths due to drug toxicity.

@@

@tbl-modelresults shows the coefficients of the predictor variables of the Model. Only the top half of this table is of interest to us, as it provides the values of the coefficient representing the intercept and the coefficient representing the deaths per year of males and each age group and their relationship with Gender Only, Age Only, and Age and Gender. We are also provided the standard error of coefficients in brackets. We can see from this table that the relationship between our 20-39 age group and 40-59 age group with age deaths is much greater than other age groups. We also see the same result when relating it to age and gender. By utilizing this we can estimate deaths for each age group and gender in the coming years due to drug toxicity.

```{r}
#| label: tbl-modelresults
#| tbl-cap: Model summary of the number deaths by gender and each age group
#| echo: false
#| eval: true

@@
